---
title: "sentiment analysis"
author: "Ghislene Adjaoute"
date: "2/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


SENTIMENT ANALYSIS
```{r}
library(tidyverse)
library(scales)
library(forcats)
library(tidytext)
```

```{r}
vyvanse <- read_rds('data/reviews/vyvanse.rds') %>%
  rowid_to_column(var='id')
```

```{r}
review<-vyvanse$comment
```

```{r}
tidy.vyvanse <- vyvanse %>%
  unnest_tokens(word,comment) 
```


```{r}
total.terms.vyvanse <- tidy.vyvanse%>%
  count(id)
```

```{r}
## plot sentiments
sentiment.orientation <- data.frame(orientation = c(rep("Positive",5),rep("Negative",5)),
                                    sentiment = c("anticipation","joy","positive","trust","surprise","anger","disgust","fear","negative","sadness"))

```

```{r}
tidy.vyvanse %>%
  count(id,word) %>%
  #inner_join(get_sentiments("bing"),by="word") %>%
  inner_join(get_sentiments("nrc"), by="word") %>%
  group_by(sentiment) %>%
  summarise(count_sentiment = n()) %>%
  ggplot(aes(x = reorder(sentiment, count_sentiment), y = (count_sentiment))) + 
  geom_bar(stat='identity') + coord_flip()

```

```{r}
## Las Vegas sentiments 
reviews <- read_rds('data/reviewsTripAll.rds')

meta.data <- reviews %>%
  select(hotel,reviewID,reviewRating)

reviewsTidy <- reviews %>%
  unnest_tokens(word,reviewText) %>%
  count(reviewID,word)

term.hotel <- reviewsTidy %>%
  inner_join(meta.data,by='reviewID') %>%
  group_by(hotel) %>%
  summarize(n.hotel=sum(n)) 

## sentiments by hotel 

bing <- get_sentiments("bing") 

hotel.sentiment <- reviewsTidy %>%
  inner_join(bing,by=c("word")) %>%
  left_join(meta.data,by='reviewID') %>%
  group_by(hotel,sentiment) %>%
  summarize(total=sum(n)) %>%
  inner_join(term.hotel,by='hotel') %>%
  mutate(relative.sentiment = total/n.hotel)


hotel.sentiment %>%
  ggplot(aes(x=sentiment,y=relative.sentiment,fill=sentiment)) + geom_bar(stat='identity') + 
  facet_wrap(~hotel)+ theme(axis.text.x = element_text(angle = 45, hjust = 1))


## plot of net sentiment
hotel.sentiment %>%
  select(sentiment,relative.sentiment,hotel) %>%
  spread(sentiment,relative.sentiment) %>%
  mutate(net.pos = positive-negative) %>%
  ggplot(aes(x=fct_reorder(hotel,net.pos),y=net.pos)) + geom_point(size=4) + coord_flip()+
  scale_y_continuous(labels=percent)+ylab('Net Positive Sentiment')+xlab('Resort')


## wider range of sentiments
nrc <- get_sentiments("nrc")

hotel.sentiment <- reviewsTidy %>%
  inner_join(nrc,by=c("word")) %>%
  left_join(meta.data,,by='reviewID') %>%
  group_by(hotel,sentiment) %>%
  summarize(total=sum(n)) %>%
  inner_join(term.hotel,by='hotel') %>%
  mutate(relative.sentiment = total/n.hotel)


hotel.sentiment %>%
  ggplot(aes(x=sentiment,y=relative.sentiment,fill=sentiment)) + geom_bar(stat='identity') + 
  facet_wrap(~hotel,ncol=3)+ theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  theme(legend.position="none")








