---
title: ''
author: "Gino Slanzi"
date: "2/29/2020"
output: html_document
---

General Methodology:
Start by doing a word frequency count:

* Are there common words that occur in most documents? Throw them out!
Stop words

  * Words related to the overall context of the documents (things like brand or product names, place names etc. )
  
  * In general, punctuation doesn't add value to this modeling. Using unnest_tokens gets rid of it.
  
  * Throw out rare words (they can’t tell anything interesting about topics anyway). This will also eliminate typos.
  
  * It is usually recommended to also stem or lemmatize your documents

  * Throw out documents with low word count (they are hard to classify)

Finally, reshape your documents into the form of a document-term matrix. This will be the input into the LDA. All of these steps can be one using the tidytext package.


```{r results='hide', message=FALSE, warning=FALSE}
#Libraries
library(tidyverse)
library(tidytext)
library(readr)
library(textstem)
library(topicmodels)
```

##### Load the data
```{r}

#upload the data into shiny
cirque <- read_csv("Data/Cirque_Train.csv")
#med <- read_csv("Ghislene/Data/drug_combine.csv")
```

##### Preprocess

```{r}
#Add id of each review:
cirque <- cirque %>% mutate(id = row_number())

#un nest tokens (tokens = 1 word)
text_cleaning_tokens <- cirque %>% 
  unnest_tokens(word, Text)

# remove numbers and signs
text_cleaning_tokens$word <- gsub('[[:digit:]]+', '', text_cleaning_tokens$word)
text_cleaning_tokens$word <- gsub('[[:punct:]]+', '', text_cleaning_tokens$word)

# Remove stoptwords
text_cleaning_tokens <- text_cleaning_tokens %>% 
  filter(!(nchar(word) == 1)) %>% 
  anti_join(stop_words)

# Remove empty rows (from the previuos cleaning process)
text_cleaning_tokens <- text_cleaning_tokens %>% filter(!(word==""))


text_cleaning_tokens <- text_cleaning_tokens %>%
  mutate(word = lemmatize_words(word))

tokens <- text_cleaning_tokens %>% 
  group_by(id) %>%
  mutate(ind = row_number()) %>%
  spread(key = ind, value = word)

tokens[is.na(tokens)] <- ""
tokens <- unite(tokens, text,-id, -Show, sep =" " )

#Remove low TF-IDf
#TF-IDF:
tokens2 <- tokens %>%
  ungroup() %>%
  unnest_tokens(word,text) %>%
  count(Show,word,sort=TRUE) %>%
  bind_tf_idf(word, Show, n) 

tf_idf0 <- tokens2 %>%
  filter(tf_idf == 0)


# Remove tfifd0
prueba <- tokens %>%
  unnest_tokens(word,text) %>%
  anti_join(tf_idf0, by="word") %>%
  count(id,word)

#prueba <- tokens %>%
#  unnest_tokens(word,text) %>%
#  count(id,word)

dtm_prueba <- prueba %>%
  cast_dtm(id, word, n)

```

```{r}
#Topic model
ap_lda <- LDA(dtm_prueba, k = 5, control = list(seed = 1234))
ap_lda



ap_topics <- tidy(ap_lda, matrix = "beta")
ap_topics


ap_top_terms <- ap_topics %>%
  group_by(topic) %>%
  top_n(25, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered()



beta_spread <- ap_topics %>%
  mutate(topic = paste0("topic", topic)) %>%
  spread(topic, beta) %>%
  filter(topic1 > .001 | topic2 > .001) %>%
  mutate(log_ratio = log2(topic2 / topic1))

beta_spread


beta_spread %>%
  top_n(25) %>%
  ggplot(aes(term, log_ratio)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_x_reordered()
```


Let's see how this goes for Drugs:

##### Load the data
```{r}

#upload the data into shiny
#cirque <- read_csv("Data/Cirque_Train.csv")
med <- read_csv("Ghislene/Data/drug_combine.csv")
```

##### Preprocess

```{r}
#Add id of each review:
med <- med %>% mutate(id = row_number()) %>%
  select(id,drug_name,comment)

#un nest tokens (tokens = 1 word)
med_text_cleaning_tokens <- med %>% 
  unnest_tokens(word, comment)

# remove numbers and signs
med_text_cleaning_tokens$word <- gsub('[[:digit:]]+', '', med_text_cleaning_tokens$word)
med_text_cleaning_tokens$word <- gsub('[[:punct:]]+', '', med_text_cleaning_tokens$word)

# Remove stoptwords
med_text_cleaning_tokens <- med_text_cleaning_tokens %>% 
  filter(!(nchar(word) == 1)) %>% 
  anti_join(stop_words)

# Remove empty rows (from the previuos cleaning process)
med_text_cleaning_tokens <- med_text_cleaning_tokens %>% filter(!(word==""))

med_text_cleaning_tokens <- med_text_cleaning_tokens %>%
  mutate(word = lemmatize_words(word))


med_tokens <- med_text_cleaning_tokens %>% 
  group_by(id) %>%
  mutate(ind = row_number()) %>%
  spread(key = ind, value = word)

med_tokens[is.na(med_tokens)] <- ""
med_tokens <- unite(med_tokens, text,-id, -drug_name, sep =" " )

#Remove low TF-IDf
#TF-IDF:
med_tokens2 <- med_tokens %>%
  ungroup() %>%
  unnest_tokens(word,text) %>%
  count(drug_name,word,sort=TRUE) %>%
  bind_tf_idf(word, drug_name, n) 

med_tf_idf0 <- med_tokens2 %>%
  filter(tf_idf == 0)

length(unique(med_tf_idf0$word))

# Remove tfifd0
prueba_med <- med_tokens %>%
  unnest_tokens(word,text) %>%
  anti_join(med_tf_idf0, by="word") %>%
  count(id,word)

prueba <- tokens %>%
  unnest_tokens(word,text) %>%
  count(id,word)

dtm_prueba_med <- prueba_med %>%
  cast_dtm(id, word, n)


```

```{r}


ap_lda_med <- LDA(dtm_prueba_med, k = 10, control = list(seed = 1234))
ap_lda_med



ap_topics_med <- tidy(ap_lda_med, matrix = "beta")
ap_topics_med


ap_top_terms_med <- ap_topics_med %>%
  group_by(topic) %>%
  top_n(25, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms_med %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered()



beta_spread <- ap_topics %>%
  mutate(topic = paste0("topic", topic)) %>%
  spread(topic, beta) %>%
  filter(topic1 > .001 | topic2 > .001) %>%
  mutate(log_ratio = log2(topic2 / topic1))

beta_spread


beta_spread %>%
  top_n(25) %>%
  ggplot(aes(term, log_ratio)) +
  geom_col(show.legend = FALSE) +
  coord_flip() +
  scale_x_reordered()
```

Another attempt with med data:

1. remove stopwords
2. create bigrams
3. remove bigrams with low tf-idf
4. run topic model

```{r}
#Add id of each review:
#med <- med %>% mutate(id = row_number()) %>%
#  select(id,drug_name,comment)


#un nest tokens (tokens = 1 word)
med_text_cleaning_tokens <- med %>% 
  unnest_tokens(word, comment)

# remove numbers and signs
med_text_cleaning_tokens$word <- gsub('[[:digit:]]+', '', med_text_cleaning_tokens$word)
med_text_cleaning_tokens$word <- gsub('[[:punct:]]+', '', med_text_cleaning_tokens$word)

# Remove stoptwords
med_text_cleaning_tokens <- med_text_cleaning_tokens %>% 
  filter(!(nchar(word) == 1)) %>% 
  anti_join(stop_words)



# Remove empty rows (from the previuos cleaning process)
med_text_cleaning_tokens <- med_text_cleaning_tokens %>% filter(!(word==""))

med_text_cleaning_tokens <- med_text_cleaning_tokens %>%
  mutate(word = lemmatize_words(word))


med_tokens <- med_text_cleaning_tokens %>% 
  group_by(id) %>%
  mutate(ind = row_number()) %>%
  spread(key = ind, value = word)

med_tokens[is.na(med_tokens)] <- ""
med_tokens <- unite(med_tokens, text,-id, -drug_name, sep =" " )

#Create Bi-grams:

med_bigrams <- med_tokens %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2)


#Remove low TF-IDf
#TF-IDF:
med_bigrams2<- med_bigrams %>%
  ungroup() %>%
  count(drug_name,bigram,sort=TRUE) %>%
  bind_tf_idf(bigram, drug_name, n) 

med_bigrams_tf_idf0 <- med_bigrams2 %>%
  filter(tf_idf == 0)

length(unique(med_bigrams_tf_idf0$bigram))

# Remove tfifd0
prueba_med_bigram <- med_tokens %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  anti_join(med_bigrams_tf_idf0, by="bigram") %>%
  count(id,bigram)


dtm_prueba_med_bigram <- prueba_med_bigram %>%
  cast_dtm(id, bigram, n)


```



```{r}
#Topic model
ap_lda_med_bigram <- LDA(dtm_prueba_med_bigram, k = 5, control = list(seed = 1234))
ap_lda_med_bigram



ap_topics_med_bigram <- tidy(ap_lda_med_bigram, matrix = "beta")
ap_topics_med_bigram


ap_top_terms_med_bigram <- ap_topics_med_bigram %>%
  group_by(topic) %>%
  top_n(25, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

ap_top_terms_med_bigram %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered()



#beta_spread_med_bigram <- ap_topics_med_bigram %>%
#  mutate(topic = paste0("topic", topic)) %>%
#  spread(topic, beta) %>%
#  filter(topic1 > .001 | topic2 > .001) %>%
#  mutate(log_ratio = log2(topic2 / topic1))
#
#beta_spread_med_bigram
#
#
#beta_spread_med_bigram %>%
#  top_n(25) %>%
#  ggplot(aes(term, log_ratio)) +
#  geom_col(show.legend = FALSE) +
#  coord_flip() +
#  scale_x_reordered()
```


What about using bigrams after taking out common words:

```{r}
eliminar_med <- unique(med_tf_idf0$word)


# create tokes and remove those words:
med_bigrams_clean <- med_tokens %>%
  unnest_tokens(bigram, text, token = "ngrams", n = 2) %>%
  separate(bigram, c("word1", "word2"), sep = " ") %>%
  filter(!word1 %in% eliminar_med) %>%
  filter(!word2 %in% eliminar_med) %>%
  unite(bigram, word1, word2, sep = " ") %>%
  count(id,bigram)

dtm_bigram <- med_bigrams_clean %>%
  cast_dtm(id,bigram,n)

#Topic model new:
#Topic model
lda_med_bigram <- LDA(dtm_bigram, k = 6, control = list(seed = 1234))
lda_med_bigram



topics_med_bigram <- tidy(lda_med_bigram, matrix = "beta")
topics_med_bigram


top_terms_med_bigram <- topics_med_bigram %>%
  group_by(topic) %>%
  top_n(25, beta) %>%
  ungroup() %>%
  arrange(topic, -beta)

top_terms_med_bigram %>%
  mutate(term = reorder_within(term, beta, topic)) %>%
  ggplot(aes(term, beta, fill = factor(topic))) +
  geom_col(show.legend = FALSE) +
  facet_wrap(~ topic, scales = "free") +
  coord_flip() +
  scale_x_reordered()

```


